A note on $\K$ of Kac---Moody groups over a field

### 2017-08-15 paper.tex
Simplified Example

\begin{example}
To produce a concrete counterexample, start with GCM 
 $A = \left(\begin{smallmatrix}
 2& -3& -2& 0\\
-1& 2& -2& 0\\
-2& -2& 2& -4\\
0& 0& -4& 2\end{smallmatrix}\right)$
  and write down SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$:
\[\widetilde{A} = \left(\begin{smallmatrix}
-1& 3& 0& 0\\
-2& 0& 2& 0\\
0& 0& 0& 0\\
0& -2& 2& 0\\
0& 0& 0& 0\\
0& 0& -4& 4
\end{smallmatrix} \right) = \left(\begin{smallmatrix}
1& 0& 0& 0& 0& 0\\
2& 1& 0& 0& 0& 0\\
0& 0& 0& 0& 1& 0\\
0& 1& 0& 1& 0& 0\\
0& 0& 0& 0& 0& 1\\
0& -2& 1& 0& 0& 0\end{smallmatrix}\right) \cdot \mathrm{diag}(-1,2,4,4) \cdot \left(\begin{smallmatrix}
1& -3& 0& 0\\
0& -3& 1& 0\\
0& -3& 0& 1\\
0& 1& 0& 0\\ \end{smallmatrix}\right) = p \cdot d \cdot q.\]
Looking at the last 2 columns of $q$ we obtain that $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd ones are even,
 hence $\K(A, F) \cong \Kmw/I \oplus \Kmw/2I \oplus \K(F)/4\K(F)$.

Now set $s = t_{43}(1) \in \SL(4, \ZZ)$, $t = t_{43}(-1) \in \SL(6, \ZZ)$ and consider the decomposition 
$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
It remains to notice that both criterions mentioned above are unable to correctly determine the 
 type of summands appearing in $\K(A, F)$ from the matrix $sq$.
\end{example}

>>>>

\begin{example}
To produce a counterexample, start with GCM 
 $A = \left(\begin{smallmatrix}
 2& -1& -2\\
-3& 2& -4\\
-4& -2& 2\end{smallmatrix}\right)$
  and write down SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$:
\[\widetilde{A} = \left(\begin{smallmatrix}
-3& 1& 0 \\
-4& 0& 2 \\
 0& -2& 4
\end{smallmatrix} \right) = \left(\begin{smallmatrix}
 1& 0& 0\\
 0& 1& 0\\
-2& 2& 1\end{smallmatrix}\right) \cdot \mathrm{diag}(1,2,2) \cdot \left(\begin{smallmatrix}
-3& 1& 0\\
-2& 0& 1\\
 1& 0& 0 \end{smallmatrix}\right) = p \cdot d \cdot q.\]
Looking at the last column of $q$ we get that $1$st and $3$rd columns of $d$ are odd while $2$nd one is even,
 hence $\K(A, F) \cong \Kmw/I \oplus \K(F)/2\K(F)$.

Now set $s:= t_{32}(1)$, $t:= t_{32}(-1) \in \SL(3, \ZZ)$ and consider the decomposition 
$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
It remains to notice that both criterions mentioned above are unable to correctly determine the 
 type of summands appearing in $\K(A, F)$ from the matrix $sq$.
\end{example}
